Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-06-16 Ben_Manuscripts/structure_paper/Draft.tex
updated draft.

  Nanostructured porous membranes made from the cross-linked hexagonal phase of
  self-assembled lyotropic liquid crystals (LLCs) are a promising material for
  selective separations. In this work, we develop an atomistic molecular model
  of an experimentally characterized LLC membrane. While it is relatively 
  straightforward to create a stable hexagonal phase model, we demonstrate that 
  closely reproducing the experimental pore structure requires a carefully 
  constructed initial configuration in order to avoid falling into metastable
  basins. We use simulated X-ray Diffraction (XRD) patterns in order to ensure 
  maximum consistency between our structures and experiment. We show that pores 
  are likely composed of 5 columns of stacked LLC monomers which surround each
  hydrophilic core. Although this system has been reported as dry, we show that
  small amounts of water are necessary to fully reproduce the experimental XRD
  pattern due to asymmetries introduced by hydrogen bonds between monomer head
  groups and water molecules. We explore the composition and structure of the 
  nanopores and reveal that there exists a composition gradient rather than a 
  hard partition between the hydrophilic and hydrophobic regions. The clearer 
  picture of the nanoscopic structure of these membranes provided in
  this study will enable a better understanding of the mechanisms of small 
  molecule transport within these nanopores.

  \end{abstract}

@@

@@

  % MRS: abstract seems a bit limited, describe more generally (and
  % briefly!) other things selective membranes are good for. The paper is primarily about selective membranes, not fracking water.  
  % It seems out of       balance to be talking about only one application.

@@

% MRS6: I would keep a paragraph about here how current membranes DON'T
% work for this purpose. But one paragraph is enough.
% BJC5: added back below paragraph.  
% MRS7: Do a pass for clarity at the sentence level.  For example ``degree of stochasticity'' is vague.
  Current commercial RO and NF membranes suffer limitations to their selectivity
  because they are unstructured. Although scalable, their fabrication involves the 
  spontaneous assembly of polymers into disordered structures which offer separation 
  pathways that are tortuous and polydisperse in size. This makes overcoming the well-known 
  permeability-selectivity tradeoff a challenge. Namely, it is difficult to increase
  the permeability of a desired molecular or atomic species, while maintaining the 
  same retention of an undesired species \cite{werber_materials_2016}.

@@

  Crosslinked lyotropic liquid crystal (LLC) membranes may be capable of
  performing highly selective separations. LLCs are amphiphilic molecules that
  have the ability to self-assemble into porous nanostructures
  \cite{smith_ordered_1997} and can be crosslinked to create mechanically
  strong membrane films with pores on the order of 1 nm in diameter
  \cite{zhou_supported_2005}. Unlike most commercial NF membranes, LLC membrane pores
  are uniform in size because they are self-assembled. 
  Since LLC membranes lack a pore size distribution, they
  inherently exhibit high selectivity due to their strict molecular weight
  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
  described in this paper are salts, and therefore lead to Donnan exclusion of ions
  in solution. The membrane gains a net surface charge when counterions from the head
  groups that line the pore walls escape into the feed solution in an effort to balance 
  the gradients of concentration and electric potential \cite{donnan_theory_1995}.

@@

  %Nanostructured porous membrane materials have become increasingly popular for
  %aqueous separations applications such as desalination and biorefinement because
  %they offer the ability to control pore architecture at the molecular scale,
  %thereby permitting the design of solute-specific separation membranes
  %\cite{humplik_nanostructured_2011}. One can acheive most membrane-based aqueous separations of
  %small molecules using reverse osmosis (RO) or nanofiltration
  %(NF) \cite{van_der_bruggen_review_2003}. While RO and NF have seen many
  %advances in the past few decades, they are far from perfect separation

@@

  Recently, researchers have learned how to macroscopically align the hexagonal
  domains which has revived research into H\textsubscript{II} phase LLC membranes.
  Previously, research efforts were focused on the Q\textsubscript{I} phase,
  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
  can align Col\textsubscript{h} hexagonal domains, created by the monomer Na-GA3C11,
  using a magnetic field with subsequent cross-linking to lock the structure in 
  place\cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could obtain
  the same result using a second technique termed soft confinement\cite{feng_thin_2016}.
  Current experimental efforts are focused on extending the method to the 
  H\textsubscript{II} phase and characterizing the performance of these newly aligned systems.

@@

% BJC5 : This is how it is described in Xunda's papers. Should I shift to something
% that doesn't rely on stacked disks? Maybe illustrate monomers stacked into
% columns instead?
% BJC6 : I will get to redo-ing this. Just takes some time to refamiliarize myself with
% the software I used to create it
  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{layer_thick.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{The LLC monomer Na-GA3C11 (a) rendered atomistically (b)
	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
	hydrophilic head groups (blue) facing towards the disk center. The disks
	assemble into hexagonally packed columnar mesophases (e).}~\label{fig:assembly}
  \end{figure}

@@

  A molecular-level understanding of LLC membrane structure, enabled by
  molecular dynamics (MD) simulations, can provide guidelines to reduce the large
  chemical space available to design monomers for creation of separation-specific
  membranes. A good molecular model should incorporate a detailed picture of the
  nanoscopic pore structure which is crucial to understanding the role of
  monomer structure in solute transport and membrane design. Models resulting
  from molecular dynamics simulations can provide the required level of detail
  (Figure \ref{fig:detail}), assuming the force fields are sufficiently accurate.
  With such an atomistic model, we can directly observe molecular-level solute
  transport and suggest governing mechanisms. We can observe how the choice of
  head group interacts with solutes of interest. We can interchange
  counterions which may influence both the pore size and the strength of the
  Donnan potential. 
  %which affects the degree to which the membrane can exclude
  %charged species at the membrane surface.

  %BJC6: is this too bold considering the work done at University of Wisconsin?
  In this study, we build a significantly more realistic atomistic model of LLC
  membranes than, to our knowledge, has ever previously been created, and explore
  what new structural information can be gained and what structure hypotheses are
  supported by this model. We validate the model using as much experimental
  information as possible. We are most interested in reproducing the conclusions
  about structure drawn from small angle X-ray scattering (SAXS)
  and wide angle X-ray scattering (WAXS) experiments as well as in matching ionic
  conductivity measurements \cite{feng_thin_2016}.

  \begin{figure}[!htb]
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.png}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
    \caption{(a) Previous understanding of the pores are essentially speculations 
    based on limited chemical and experimental data. (b) We use a detailed molecular 
    model in this paper in order to appropriately model the pore's complex architecture
    which is crucial to understanding the mechanism of solute transport. In both 
    pictures, the head group region is colored blue and the tail region is colored cyan.}~\label{fig:detail}
  \end{figure}

  In this paper, we develop a molecular model of the Col\textsubscript{h} assembly 
  formed by Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
  phase is a simpler starting point. The system has no water which allowed us
  to simulate longer timescales, and there exists detailed experimental
  characterization of the fully aligned state, including 2D wide-angle X-ray
  scattering (WAXS) patterns (Figure~\ref{fig:WAXS}) which are useful for reconstructing 
  structural data. We will use this Col\textsubscript{h} model in order to build an 
  H\textsubscript{II} model in the future.
  %The two phases appear to share similar structural characteristics since the
  %pore spacings in each system are in close agreement
  %\cite{feng_thin_2016,resel_structural_2000}.

@@

	\item \textit{R-double}: A weak intensity line, located at exactly half
	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to real
	space periodicity of 7.4 \AA. Since this reflection corresponds to double
	the spacing of R-$\pi$ in real space, we will refer to this reflection as R-double. 
	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
	rings along the z axis\cite{feng_scalable_2014}, meaning that if one traces the 
	positions of the aromatic rings with a helical curve, then for each full turn 
	in the helix, one will encounter two aromatic rings.

@@

  Despite having structural data, there is still information which experiment cannot
  definitively answer. There are a number of structural questions we wish to answer in this 
  article. We want to know:
  \begin{enumerate}
    \item What is the density of monomers that pack around each hydrophilic core? 
    \label{point:monomernum}

@@

    %MRS7: is this really a liquid crystalline system, even if it is made of liquid crystal monomers? Should we say
    % in many liquid crystal systems?
    %BJC5: changed to 'many liquid crystalline systems'
 	We are careful to avoid the term 'layers' since many liquid crystalline systems
 	have long range order in 1 or 2 spatial dimensions and short range order in 	
 	the other dimensions.~\cite{chaikin_principles_1995}  % page 58
 	In the system we are studying, there are long-range 2D correlations in the 
 	hexagonal array of pores (xy plane) and short range z-direction correlations between 
        stacked columns of monomers. In this study, we use our atomistic molecular model
        to study how the system's structure is affected by the density of these monomer columns
        that surround each pore's hydrophilic core.

@@

	On the short timescales accessible to MD (even the 100's of nanoseconds of simulation 
	peformed here are short compared to experimental timescales), we observe distinct metastable
	configurations which depend on starting configuration. We simulated XRD patterns of our system and 
	compared them to experimental 2D WAXS patterns (Figure~\ref{fig:WAXS}) so that we ensure our
	model creates a nanoscopic chemical environment maximally consistent with experiment within 
	the constraints	of our forcefield. Using this approach, we are able to confirm some previous
	interpretations	of the WAXS pattern and refute others.

	%BJC5: I could add brief references to other LLC studies which look at hexagnoal phase, but
	% without scrutinizing the structural details. In other words, other authors have gotten 
	% hexagonal phases with self-assembly, but they can't prove that their structure is the same
	% as experiment. The best there are, are 1D structure factors in the small angle regime.

@@

	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
	ambient water are leached into the system. The hydrogen bonding network formed by the 
	water may play a role in structuring the pore. We used simulated X-ray diffraction (XRD) patterns
	to see if there is any meaningful structural difference between a "dry" and a "wet" system.

	\item What is the chemical composition of the pores?\label{point:composition}

@@

  We generated an ensemble of characteristic, low-energy vacuum monomer
  configurations by applying a simulated annealing process to a
  parameterized monomer. We cooled monomers from 1000K to 50K over 10
  nanoseconds. We randomly pulled a low energy configuration from the
  trajectory then reassigned charges using \texttt{molcharge}. Using the new
  charges, we annealed the monomer system again and pulled a random monomer
  configuration from the trajectory which we used for full system
  construction (Figure~\ref{fig:python}a). See section S\ref{S-section:parameterization} 
  for further detail.

@@

  The timescale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  calling for a more efficient way to build the system. Previous work has shown
  a coarse-grained model self assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system (See section S\ref{S-section:self_assembly}). 
  To bypass the slow self-assembly process, we use Python scripts to assemble monomers
  into a structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:python}).

@@

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended
  periodically. Each pore is made of columns of stacked monomers with periodic
  continuity along the pore axis, avoiding any edge effects and creating an
  infinite length pore ideal for studying transport. We prefer a small number of stacked
  monomers in order to reduce computational cost and to allow us to look at
  longer timescales. Ultimately, we chose to build a system with 20 monomers
  per column in order to minimize finite size effects with reasonable computational expense 
  and to obtain sufficient resolution when simulating XRD patterns (see further discussion
  in section S\ref{S-section:monomers_per_column}).

@@

  When constructing an initial configuration, there are a number of variables
  which require careful consideration while placing monomers. The equilibrium
  configuration is sensitive to some while insensitive to others. The starting
  pore radius, defined as the distance of a chosen head group carbon from the
  pore's central axis, does not influence the equilibrium structure if one choses
  a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
  configurations. The initial distance between pores, within a wide range, also has 
  little effect on the the equilibrated structure. However, one should not start them
  too close or there will be high energy repulsions during early equilibration. We 
  chose an initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
  of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
  Supporting information, section S\ref{S-section:initial_config_dependence}. The 
  distance between vertically stacked monomers, the xy position of monomers with respect 
  to vertically adjacent monomers, and the number of columns per pore do influence the 
  equilibrated structure and require further justification for their choices. We rely on 
  experimental data to inform them.

  We chose the vertical spacing between monomers for the initial configuration based
  on R-$\pi$ and then allowed the system to readjust during equilibration. We rotated 
  each monomer so the plane of its aromatic head group would be coplanar with the xy plane. We
  explored three different initial monomer spacings. The first is exactly
  equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
  the z-direction. We explore a second system with an initial spacing of 5
  \AA. We briefly explored a third system with an initial spacing of 10
  \AA. However this spacing yields non-physical behavior which is detailed in the 
  Supporting Information, section S\ref{S-section:initial_dbwl}.

@@

  We chose the relative orientation between vertically adjacent monomers in each column 
  based on clues from diffraction data as well as the various known stacking modes of 
  benzene and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
  \cite{sinnokrot_estimates_2002}. We ruled out the T-shaped configuration
  because its $\sim$5 \AA~equilibrium stacking distance \cite{sinnokrot_estimates_2002}
  is inconsistent with R-$\pi$. It is also infeasible for the monomers to orient in the 
  T-shaped conformation because of the bulky tail groups. We explored the system's 
  preference towards the sandwiched vs. parallel displaced stacking modes in some detail.
  Both have reported stacking distances near the R-$\pi$ value of 3.7 \AA. Head groups in
  our sandwiched initial configuration stack directly on top of each other while
  head groups in the parallel displaced initial configuration stack with an offset
  of $180^\circ/ncol$ where $ncol$ is the number of columns per pore. See Figure 
  S~\ref{S-fig:stacking} for a detailed illustration of the initial configurations in each mode.

@@

  \subsection{Equilibration}
  %MRS7: could put this mostly in supporting. 
  %BJC6: cut in half
  We developed equilibration schemes for creating dry and wet configurations. Both
  schemes start with an initial configuration generated according to the previous
  guidelines. For wet systems, we added the desired concentration of water to 
  the initial configuration and carried out equilibration in the same way
  as the dry systems. First, we fixed monomer head groups in place using position
  restraints with a force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We gradually
  released the position restraints by decreasing the force constants over a series
  of NVT simulations. We allowed the resulting unrestrained structure to equilibrate for
  5 ns in the NPT ensemble with pressure controlled by the berendsen barostat 
  followed by NPT equilibration simulations run for at least 400 ns using the 
  Parrinello-Rahman barostat. More precise details are available in 
  section S~\ref{S-section:equilibration}.

@@

  We explored the pores' compositions by measuring the average number densities
  of various monomer components as a function of distance from the pore centers.
  We looked at the average number density of sodium ions, aromatic rings and 
  carbon atoms making up the monomer tails. We binned the radial distance of all
  atoms in each group from the pore centers, then normalized by the volume of the
  annulus defined by the bin edges and the z box vector (See Figure~S\ref{S-fig:rdf_diagram}).

@@

%  R-alkanes add together to boost the overall signal at interesecting values of

@@

  \section{Conclusion}

>>>>

  Nanostructured porous membranes made from the cross-linked hexagonal phase of
  self-assembled lyotropic liquid crystals (LLCs) are a promising material for
  selective separations. In this work, we investigate an experimentally characterized 
  LLC membrane using an atomistic molecular model. 
  %MRS8: I think this is a little too subtle a point to be making for the abstract. 
  %I added a bit different spin on this at the end of the abstract to gesture towards the idea. Thoughts?
  %While it is relatively 
  %straightforward to create a stable hexagonal phase using atomistic modeling, we demonstrate that 
  %closely reproducing the experimental pore structure requires a carefully 
  %constructed initial configuration in order to avoid falling into metastable
  %basins. 
  We use simulated X-ray diffraction (XRD) patterns in order to ensure 
  maximum consistency between our structures and experiment. We show that pores 
  are likely composed of 5 columns of stacked LLC monomers which surround each
  hydrophilic core. Although this system has been reported as dry, we show that
  small amounts of water are necessary to fully reproduce the experimental XRD
  pattern due to asymmetries introduced by hydrogen bonds between monomer head
  groups and water molecules. We explore the composition and structure of the 
  nanopores and reveal that there exists a composition gradient rather than a 
  abrupt partition between the hydrophilic and hydrophobic regions. A caveat is 
  that the time scales of the dynamics are extremely long for this system, 
  requiring starting from a range of alternative initial configurations and 
  careful examination of the metastable states observed.
  The clearer picture of the nanoscopic structure of these membranes provided in
  this study will enable a better understanding of the mechanisms of small 
  molecule transport within these nanopores.
  \end{abstract}

@@

  % MRS8: intro still seems a bit limited, describe more generally
  % (and briefly!) other things selective membranes are good for. The
  % paper is primarily about selective membranes, not fracking
  % water. See elimalech paper for reviews, and add a number of more
  % citations.

@@

@@

% MRS6: I would keep a paragraph about here how current membranes DON'T
% work for this purpose. But one paragraph is enough.
% BJC5: added back below paragraph.  
% MRS7: Do a pass for clarity at the sentence level.  For example ``degree of stochasticity'' is vague.
% MRS8: ``because they are unstructured'' lacks detail.  NF has some structure, since there are irregular pores. Check some other reviews and see the points they cover?
  Current commercial RO and NF membranes suffer limitations to their selectivity
  because they are unstructured. Although scalable, their fabrication involves the 
  spontaneous assembly of polymers into disordered structures which offer separation 
  pathways that are tortuous and polydisperse in size. This makes overcoming the well-known 
  permeability-selectivity tradeoff a challenge. Namely, it is difficult to increase
  the permeability of a desired molecular or atomic species, while maintaining the 
  same retention of an undesired species \cite{werber_materials_2016}.

@@

%MRS8: preliminary evidence has shown they may be?  It's more than a guess.
  Crosslinked lyotropic liquid crystal (LLC) membranes may be capable of
  performing highly selective separations. LLCs are amphiphilic molecules that
  have the ability to self-assemble into porous nanostructures
  \cite{smith_ordered_1997} and can be crosslinked to create mechanically
  strong membrane films with pores on the order of 1 nm in diameter
  \cite{zhou_supported_2005}. Unlike most commercial NF membranes, LLC membrane pores
  are uniform in size because they are self-assembled. 
  Since LLC membranes lack a pore size distribution, they
  inherently exhibit high selectivity due to their strict molecular weight
  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
  examined in this paper are salts, and therefore lead to Donnan exclusion of ions
  in solution. The membrane gains a net surface charge when counterions from the head
  groups that line the pore walls escape into the feed solution in an effort to balance 
  the gradients of concentration and electric potential \cite{donnan_theory_1995}.

@@

  %Nanostructured porous membrane materials have become increasingly popular for
  %aqueous separations applications such as desalination and biorefinement because
  %they offer the ability to control pore architecture at the molecular scale,
  %thereby permitting the design of solute-specific separation membranes
  %\cite{humplik_nanostructured_2011}. One can achieve most membrane-based aqueous separations of
  %small molecules using reverse osmosis (RO) or nanofiltration
  %(NF) \cite{van_der_bruggen_review_2003}. While RO and NF have seen many
  %advances in the past few decades, they are far from perfect separation

@@

  Recently, researchers have learned how to macroscopically align the hexagonal
  domains which has revived research into H\textsubscript{II} phase LLC membranes.
  Previously, research efforts were focused on the Q\textsubscript{I} phase,
  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
  can align Col\textsubscript{h} hexagonal domains, created by the monomer Na-GA3C11,
  using a magnetic field with subsequent cross-linking to lock the structure in 
  place\cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could obtain
  the same result using a second technique termed soft confinement\cite{feng_thin_2016}.
  %MRS8: maybe say what it is, not just what it's named? 
  Current experimental efforts are focused on extending the method to the 
  H\textsubscript{II} phase and characterizing the performance of these newly aligned systems.

@@

% BJC5 : This is how it is described in Xunda's papers. Should I shift to something
% that doesn't rely on stacked disks? Maybe illustrate monomers stacked into
% columns instead?
% BJC6 : I will get to redo-ing this. Just takes some time to refamiliarize myself with
% the software I used to create it
%MRS8: sound good.
  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{layer_thick.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{The LLC monomer Na-GA3C11 (a) rendered atomistically (b)
	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
	hydrophilic head groups (blue) facing towards the disk center. The disks
	assemble into hexagonally packed columnar mesophases (e).}~\label{fig:assembly}
  \end{figure}

@@

  A molecular-level understanding of LLC membrane structure, enabled by
  molecular dynamics (MD) simulations, can provide guidelines to reduce the large
  chemical space available to design monomers for creation of separation-specific
  membranes. Useful molecular-level modeling should incorporate a detailed picture of the
  nanoscopic pore structure which is crucial to understanding the role of
  monomer structure in solute transport and membrane design. 
Atomistic molecular dynamics simulations can provide the required level of detail
  (Figure \ref{fig:detail}), assuming the force fields are sufficiently accurate.
  With such an atomistic model, we can directly observe molecular-level solute
  transport and suggest governing mechanisms. We can observe how the choice of
  head group interacts with solutes of interest. We can interchange
  counterions which may influence both the pore size and the strength of the
  Donnan potential. 
  %which affects the degree to which the membrane can exclude
  %charged species at the membrane surface.

  %BJC6: is this too bold considering the work done at University of Wisconsin?
  %MRS8: Maybe take out significantly
  In this study, we achieve a %significantly 
  more realistic atomistic description of LLC
  membranes than, to our knowledge, has ever previously been created, and explore
  what new structural information can be gained and what structure hypotheses are
  supported by this model. We validate the results using as much experimental
  information as possible. We are most interested in reproducing the conclusions
  about structure drawn from small angle X-ray scattering (SAXS)
  and wide angle X-ray scattering (WAXS) experiments as well as in matching ionic
  conductivity measurements \cite{feng_thin_2016}.

  \begin{figure}[!htb]
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.png}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
    \caption{(a) Previous understanding of the pores are essentially speculations 
    based on limited chemical and experimental data. (b) We use detailed molecular 
    modeling in this paper in order to appropriately model the pore's complex architecture
    which is crucial to understanding the mechanism of solute transport. In both 
    pictures, the head group region is colored blue and the tail region is colored cyan.}~\label{fig:detail}
  \end{figure}

  In this paper, we perform molecular modeling of the Col\textsubscript{h} assembly 
  formed by Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
  phase is a simpler starting point. The system 
  %MRS8: check rephrasing on this, since we do say later it does have some water
  %has no water 
  is not assembled in aqueous phase
  which allowed us to simulate longer timescales, and there exists detailed experimental
  characterization of the fully aligned state, including 2D wide-angle X-ray
  scattering (WAXS) patterns (Figure~\ref{fig:WAXS}) which are useful for reconstructing 
  structural data. 
  %MRS8: I started tweaking the below, but it might be better just to eliminate.
  % Modeling of Col\textsubscript{h} will help in modeling 
  %H\textsubscript{II} in the future.
  %The two phases appear to share similar structural characteristics since the
  %pore spacings in each system are in close agreement
  %\cite{feng_thin_2016,resel_structural_2000}.

@@

	\item \textit{R-double}: A weak intensity line, located at exactly half
	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to real
	space periodicity of 7.4 \AA. Since this reflection corresponds to double
	the spacing of R-$\pi$ in real space, we will refer to this reflection as R-double. 
	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
	rings along the $z$ axis\cite{feng_scalable_2014}, meaning that if one traces the 
	positions of the aromatic rings with a helical curve, then for each full turn 
	in the helix, one will encounter two aromatic rings.

@@

  Despite having structural data, there is still information which experiment cannot
  definitively answer. 
  %MRS8: grammatically a bit redundant.
  %There are a number of structural questions we wish to answer in this article. 
  Specifically, we want to know:
  \begin{enumerate}
    \item What is the density of monomers that pack around each hydrophilic core? 
    \label{point:monomernum}

@@

    %MRS7: is this really a liquid crystalline system, even if it is made of liquid crystal monomers? Should we say
    % in many liquid crystal systems?
    %BJC5: changed to 'many liquid crystalline systems'
 	We are careful to avoid the term 'layers' since many liquid crystalline systems
 	have long range order in 1 or 2 spatial dimensions and short range order in 	
 	the other dimensions.~\cite{chaikin_principles_1995}  % page 58
 	In the system we are studying, there are long-range 2D correlations in the 
 	hexagonal array of pores (xy plane) and short range z-direction correlations between 
        stacked columns of monomers. In this study, we use atomistic molecular modeling
        to study how the system's structure is affected by the density of these monomer columns
        that surround each pore's hydrophilic core.

@@

	On the short timescales accessible to MD (even the 100's of nanoseconds of simulation 
	performed here are short compared to experimental timescales), we observe distinct metastable
	configurations which depend on starting configuration. We simulated XRD patterns of our system and 
	compared them to experimental 2D WAXS patterns (Figure~\ref{fig:WAXS}) so that we ensure our
	model creates a nanoscopic chemical environment maximally consistent with experiment within 
	the constraints	of our forcefield. Using this approach, we are able to confirm some previous
	interpretations	of the WAXS pattern and refute others.

	%BJC5: I could add brief references to other LLC studies which look at hexagonal phase, but
	% without scrutinizing the structural details. In other words, other authors have gotten 
	% hexagonal phases with self-assembly, but they can't prove that their structure is the same
	% as experiment. The best there are, are 1D structure factors in the small angle regime.

@@

	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
	ambient water are 
        %leached 
        absorbed
        into the system. The hydrogen bonding network formed by the 
	water may play a role in structuring the pore. We used simulated X-ray diffraction (XRD) patterns
	to see if there is any meaningful structural difference between a "dry" and a "wet" system.

	\item What is the 
          %MR8: chemical composition is a bit ambiguous; implies mole fractions, which isn't what we mean
          %chemical composition 
          detailed atomistic structure of the pores?\label{point:composition}

@@

  We generated an ensemble of characteristic, low-energy vacuum monomer
  configurations by applying a simulated annealing process to a
  parameterized monomer. We cooled monomers from 1000K to 50K over 10
  nanoseconds. We randomly pulled a low energy configuration from the
  trajectory then reassigned charges using \texttt{molcharge}. Using the new
  charges, we annealed the monomer system again and pulled a random monomer
  configuration from the trajectory which we used for full system
  construction (Figure~\ref{fig:python}a). See section S-\ref{S-section:parameterization} 
  for further detail of the parameterization process.

@@

  The timescale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  calling for a more efficient way to build the system. Previous work has shown
  a coarse-grained model self assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system (see section S-\ref{S-section:self_assembly}). 
  To bypass the slow self-assembly process, we use Python scripts to assemble monomers
  into a structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:python}).

@@

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended
  periodically. Each pore is made of columns of stacked monomers with periodic
  continuity along the pore axis, avoiding any edge effects and creating an
  infinite length pore ideal for studying transport. We prefer a small number of stacked
  monomers in order to reduce computational cost and to allow us to look at
  longer timescales. Ultimately, we chose to build a system with 20 monomers
  per column in order to minimize finite size effects with reasonable computational expense 
  and to obtain sufficient resolution when simulating XRD patterns (see further discussion
  in section S-\ref{S-section:monomers_per_column}).

@@

  When constructing an initial configuration, there are a number of variables
  which require careful consideration while placing monomers. The equilibrium
  configuration is sensitive to some while insensitive to others. We find the starting
  pore radius, defined as the distance of a chosen head group carbon from the
  pore's central axis, does not influence the equilibrium structure if one chooses
  a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
  configurations. The initial distance between pores, within a wide range, also has 
  little effect on the the equilibrated structure. However, one should not start them
  too close or there will be high energy repulsions during early equilibration. We 
  chose an initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
  of 4.12 nm. A sensitivity analysis of both parameters is presented in the 
  Supporting information, section S-\ref{S-section:initial_config_dependence}. The 
  distance between vertically stacked monomers, the xy position of monomers with respect 
  to vertically adjacent monomers, and the number of columns per pore do influence the 
  equilibrated structure and require further justification for their choices. We rely on 
  experimental data to inform them.

  We chose the vertical spacing between monomers for the initial configuration based
  on R-$\pi$ and then allowed the system to readjust during equilibration. We rotated 
  each monomer so the plane of its aromatic head group would be coplanar with the xy plane. We
  explored three different initial monomer spacings. The first is exactly
  equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
  the z-direction. We explore a second system with an initial spacing of 5
  \AA. We briefly explored a third system with an initial spacing of 10
  \AA. However this spacing yields non-physical behavior which is detailed in the 
  Supporting Information, section S-\ref{S-section:initial_dbwl}.

@@

  We chose the relative orientation between vertically adjacent monomers in each column 
  based on clues from diffraction data as well as the various known stacking modes of 
  benzene and substituted benzene rings: sandwiched, parallel-displaced and T-shaped
  \cite{sinnokrot_estimates_2002}. We ruled out the T-shaped configuration
  because its $\sim$5 \AA~equilibrium stacking distance \cite{sinnokrot_estimates_2002}
  is inconsistent with R-$\pi$. It is also infeasible for the monomers to orient in the 
  T-shaped conformation because of the bulky tail groups. We explored the system's 
  preference towards the sandwiched vs. parallel displaced stacking modes in some detail.
  Both have reported stacking distances near the R-$\pi$ value of 3.7 \AA. Head groups in
  our sandwiched initial configuration stack directly on top of each other while
  head groups in the parallel displaced initial configuration stack with an offset
  of $180^\circ/ncol$ where $ncol$ is the number of columns per pore. See Figure 
  S-\ref{S-fig:stacking} for a detailed illustration of the initial configurations in each mode.

@@

  \subsection{Equilibration}
  %MRS7: could put this mostly in supporting. 
  %BJC6: cut in half
  We developed equilibration schemes for creating dry and wet configurations. Both
  schemes start with an initial configuration generated according to the previous
  guidelines. For wet systems, we added the desired concentration of water to 
  the initial configuration and carried out equilibration in the same way
  as the dry systems. First, we fixed monomer head groups in place using position
  restraints with a force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We gradually
  released the position restraints by decreasing the force constants over a series
  of NVT simulations. We allowed the resulting unrestrained structure to equilibrate for
  5 ns in the NPT ensemble with pressure controlled by the berendsen barostat 
  followed by NPT equilibration simulations run for at least 400 ns using the 
  Parrinello-Rahman barostat. 
  %More precise details are 
  More equilibration details are 
  available in 
  section S-\ref{S-section:equilibration}.

@@

  We explored the pores' compositions by measuring the average number densities
  of various monomer components as a function of distance from the pore centers.
  We looked at the average number density of sodium ions, aromatic rings and 
  carbon atoms making up the monomer tails. We binned the radial distance of all
  atoms in each group from the pore centers, then normalized by the volume of the
  annulus defined by the bin edges and the z box vector (See Figure~S-\ref{S-fig:rdf_diagram}).

@@

%  R-alkanes add together to boost the overall signal at intersecting values of

@@

  \section{Conclusions}
